\TITLE

### 2020-12-31 response-v3-content.tex

%\end{figure}

}

\REVIEW{DONE}{Table 4: keep the number of digits consistent.}{
   The digits have been padded with the missing 0 to make them all
    the same length}

\REVIEW{DONE}{Reproducibility: submit data/code/README in a
  compressed file as supplementary material, or put them in a public
  repo and give the link under an unnumbered section Supplementary
  Material.}
  {A supplementary section was added with pointers to all available code and data. Usage of the data is restricted prior to publication of this paper.}

### 2020-12-31 vonLaszewski-covid.tex
Updates from Overleaf

>>>>

The code and paper document represented to implement AICov are contained in several repositories:

\begin{enumerate}
    \item The entire cloudmesh code on which the cloud based implementation of the AICov framework is based and contains over 70 contributors is available publicly at \url{https://github.com/cloudmesh}. Cloudmesh contains a number of modules that dependent on the users access to cloud resources can be customized. A detailed manual about the configuration is available at \url{https://cloudmesh.github.io/cloudmesh-manual/}

    \item The entire COVID-19 analysis is based leverages cloudmesh and uses Jupyter notebooks to coordinate its workflow as discussed in the architecture Figure \ref{fig:arch}. The code and data for the results presented in this paper are located in the repository at \url{https://github.com/cloudmesh/cloudmesh-covid}.

    The data was analysed on a variety of supercomputing resources including an allocation of 20 compute nodes that were utilized to execute the  repeated model creation to assure reproducible results.

    However, as a publication is pending, at this time, the use of the data is copyrighted and can not be used for other publications without contacting the authors. The data gathering and analysis is a significant intellectual contribution and we like to avoid that the data is taken before we have not secured a publication.

    \item The entire paper is located in \LaTeX source in the github repository \url{https://github.com/cyberaide/paper-covid}. This repository will be open sourced after acceptance of publication. If desireed the authors can grant acess to this repository prior to publication. Please contact the corresponding author.

\end{enumerate}
